Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-07 Ben_Manuscripts/Paper1/Outline.tex
added a conclusion

  Experimental WAXS measurements encode all structural details. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-pi.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the qz value of
	R-pi (qz = 0.85 \angstrom$^-1$), corresponding to a 
        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	different configurations indicating that we have found more than one metastable
	free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom 
	layer spacing implied by R-pi are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
        %MRS: the basin is with respect to. 
	%BJC: added sentence to beginning of paragraph
        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
        %\item We will refer to this system as
        %MRS: maybe Basin O and Basin C for open and closed?
	%BJC: That works but 'capital oh' might get confused with zero
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
        %MRS: see above for clarifying ``basins''.
	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.  %MRS: remind people why.
  \end{itemize}

@@

  We varied the initial relative interlayer orientation between sandwiched and 
  parallel-displaced based on our knowledge of the stability of the two
  pi-stacking modes.
  \begin{itemize}
  	\item We generated simulated X-ray diffraction patterns using simulation trajectories from the highly
	restrained initial configurations created during equilibration
	\item The simulated patterns establish a difference between the two stacking 
	modes (Figure~\ref{fig:XRDrestrained}).
	\item In each pattern, R-alkanes is present at a distance of $\approx
	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
  	\item R-pi is also present in each pattern, although it appears to 
	intersect R-alkanes because the spacing between aromatic rings is 
	similar to the alkane chain packing.
        %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
	%BJC: okay added some more specific language
	\item The difference in aromatic ring spacing between experiment and
	simulation is likely a result of the inability of GAFF to properly handle
	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
	\item The sandwiched configuration shows R-spots in the expected location.
	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
	\item The parallel displaced configuration contains two lines of high 
	intensity with maximum intensity occurring where they intersect the alkane
	chain region due to constructive interference between the two features.
	\item The lines are located where one would expect to see R-helix and, 
	perhaps coincidentally, the intersection with R-alkanes occurs where one 
	would expect to see R-spots.
	%BJC: might save the following sentence for equilibrium trajectories
	\item As the simulation is progressed, the full line begins to fade 
	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
	where R-helix exists.
  \end{itemize}

@@

  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.  Something to think about.
  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
  %MRS: make sure the figures are comparable.  Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns produced from equilibrated MD trajectories shows the most consistency
  with the sandwiched configuration in Basin A.
  \begin{itemize}
  	\item Systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom apart in order to guide it towards Basin B.
	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
	\item For ease of reference, the third system will be referred to as the disordered system. 
%BJC: omit and call it basin B
%MRS or just be consistent from the beginning.  Or call Basins O and D          
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
	%BJC: maybe break into a separate paragraph starting here
	\item The equilibrated parallel displaced structure exhibits R-alkanes and
	R-pores in the expected locations. 
	\item Due to low resolution, making out the individual spots of R-pores is
	challenging and can be validated upon full spherical integration of the 3D 
	structure factor. However, the same information can be extracted by measuring 
	the pore spacing as described earlier.
	\item R-pi is also present, intersecting R-alkanes at a lower q value than
	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
	opposed to 3.7 \angstrom.
	\item R-helix and R-spots are also both missing.
	\item The line which intersected both of these features in the restrained 
	simulations faded upon equilibration which suggests that monomers in the 
	parallel-displaced configuration may not give rise to the experimental WAXS 
	pattern seen.
	\item Simulated XRD of the sandwiched configuration contains all features 
	except for R-helix.
	\item Most notably, R-spots appears in the expected location, which suggests 
	that there is something intrinsic to the sandwiched packing that gives rise 
	to such features. 
	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
	R-helix, R-pi and R-spots are not present.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{(a) All major features except R-helix are present in
	XRD patterns resulting from an equilibrated sandwiched configuration 
	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
	(b) All major features execpt R-spots are present in XRD patterns 
	resulting from an equilibrated parallel displaced configuration in Basin A.
	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
	are the only major features present in XRD patterns resulting from an 
	equilibrated disordered phase}\label{fig:XRDsim}
  \end{figure}

@@

>>>>

  Experimental WAXS measurements encode all structural details. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-$\pi$.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the qz value of
	R-$\pi$ (qz = 0.85 \angstrom$^-1$), corresponding to a 
        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	different configurations indicating that we have found more than one metastable
	free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom 
	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
        %MRS: the basin is with respect to. 
	%BJC: added sentence to beginning of paragraph
        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
        %\item We will refer to this system as
        %MRS: maybe Basin O and Basin C for open and closed?
	%BJC: That works but 'capital oh' might get confused with zero
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
        %MRS: see above for clarifying ``basins''.
	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.  %MRS: remind people why.
  \end{itemize}

@@

  We varied the initial relative interlayer orientation between sandwiched and 
  parallel-displaced based on our knowledge of the stability of the two
  pi-stacking modes.
  \begin{itemize}
  	\item We generated simulated X-ray diffraction patterns using simulation trajectories from the highly
	restrained initial configurations created during equilibration
	\item The simulated patterns establish a difference between the two stacking 
	modes (Figure~\ref{fig:XRDrestrained}).
	\item In each pattern, R-alkanes is present at a distance of $\approx
	1.5$ \angstrom \textsuperscript{-1} (4.2 \angstrom in real space).
  	\item R-$\pi$ is also present in each pattern, although it appears to 
	intersect R-alkanes because the spacing between aromatic rings is 
	similar to the alkane chain packing.
        %MRS: for above, may need to clarify that this is in simulation, which is different than experiment.
	%BJC: okay added some more specific language
	\item The difference in aromatic ring spacing between experiment and
	simulation is likely a result of the inability of GAFF to properly handle
	aromatic interactions. %MRS: provide citations, some mechanistic reasoning.
	\item The sandwiched configuration shows R-spots in the expected location.
	\item A faint reflection is present in the location of R-helix %BJC: but it fades upon further simulation.
	\item The parallel displaced configuration contains two lines of high 
	intensity with maximum intensity occurring where they intersect the alkane
	chain region due to constructive interference between the two features.
	\item The lines are located where one would expect to see R-helix and, 
	perhaps coincidentally, the intersection with R-alkanes occurs where one 
	would expect to see R-spots.
	%BJC: might save the following sentence for equilibrium trajectories
	\item As the simulation is progressed, the full line begins to fade 
	(Figure~\ref{fig:XRDsim}). Most significantly, the line is no longer present
	where R-helix exists.
  \end{itemize}

@@

  %MRS: one thought: maybe organize it a different way -- it's not the disordered (and go through the anlysis there), and then separately show that it's more likely the sandwich.  Something to think about.
  %MRS: anyway, this is the key part of the paper, so clarity and organization important.
  %MRS: make sure the figures are comparable.  Could someone look at the figures, and see immediately what you are explaining -- for example, experiment and fully equilibrated disordered, sandwich and parallel displaced all in a row?
  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns produced from equilibrated MD trajectories shows the most consistency
  with the sandwiched configuration in Basin A.
  \begin{itemize}
  	\item Systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom apart in order to guide it towards Basin B.
	% BJC: I've done an additional offset disordered system which goes to Basin B but I think that will confuse the point
	\item For ease of reference, the third system will be referred to as the disordered system. 
%BJC: omit and call it basin B
%MRS or just be consistent from the beginning.  Or call Basins O and D          
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
	%BJC: maybe break into a separate paragraph starting here
	\item The equilibrated parallel displaced structure exhibits R-alkanes and
	R-pores in the expected locations. 
	\item Due to low resolution, making out the individual spots of R-pores is
	challenging and can be validated upon full spherical integration of the 3D 
	structure factor. However, the same information can be extracted by measuring 
	the pore spacing as described earlier.
	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
	opposed to 3.7 \angstrom.
	\item R-helix and R-spots are also both missing.
	\item The line which intersected both of these features in the restrained 
	simulations faded upon equilibration which suggests that monomers in the 
	parallel-displaced configuration may not give rise to the experimental WAXS 
	pattern seen.
	\item Simulated XRD of the sandwiched configuration contains all features 
	except for R-helix.
	\item Most notably, R-spots appears in the expected location, which suggests 
	that there is something intrinsic to the sandwiched packing that gives rise 
	to such features. 
	\item Finally, the disordered structure exhibits R-alkanes and R-pores but 
	R-helix, R-$\pi$ and R-spots are not present.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{(a) All major features except R-helix are present in
	XRD patterns resulting from an equilibrated sandwiched configuration 
	in Basin A. R-$\pi$ intersescts R-alkanes. R-helix faded during equilbration.
	(b) All major features execpt R-spots are present in XRD patterns 
	resulting from an equilibrated parallel displaced configuration in Basin A.
	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
	are the only major features present in XRD patterns resulting from an 
	equilibrated disordered phase}\label{fig:XRDsim}
  \end{figure}

@@

  We have used a detailed molecular model of the Col\subscript{h} phase formed by NA-GA3C11
  in order to study the nanoscopic structure.
  \begin{itemize}
  	\item While there have been efforts to model formation of various liquid crystalline 
	phases with molecular dynamics, to our knowledge there have been no studies which 
	attempt to examine their structure with the same level of detail presented here.
	\item We have confirmed that monomers stay partitioned in layers.
	\item We were able to deduce that layers are composed of 5 monomers.
	\item We have identified two metastable basins which each consist of a set of 
	similar monomer configurations characterized by the degree of order in the pore region.
	\item We verified that the basins are not separate phases.
	\item We have explored the affect of two different pi-stacking modes on the equilibrated
	membrane strucure. 
	\item Simulated diffration patterns generated from MD trajectories suggest that
	the offset configuration produces a structure with the closest match to experiment. 
	\item Even though our model only answers these questions for a system created by 
	NA-GA3C11, it can be adapted to other study systems formed by other LCs with 
	little extra effort. 
  \end{itemize}
